География названий юридических фирм в России

### 2024-07-12 law-firms-names/conference-paper/Conference-slides.qmd
Reorganize law firms names folder to separate conference paper from journal article, add current code and data on journal article, #4

library(dplyr)
library(ggplot2)
library(knitr)
library(readr)
library(sf)
library(spatstat)
library(stringr)
library(tidyr)
```

@@

# load the data
data <- read_csv("../../ru-smb-companies/legal/panel.csv")
cluster_labels <- read_csv("cluster_labels.csv")
vectors <- read_csv("names_vectors.csv")
ru <- st_read("ru.geojson")

>>>>

library(dplyr)
library(ggplot2)
library(here)
library(knitr)
library(readr)
library(sf)
library(spatstat)
library(stringr)
library(tidyr)
```

@@

# load the data
data <- read_csv(here("../../ru-smb-companies/legal/panel.csv"))
cluster_labels <- read_csv(
  here("conference-paper", "cluster-labels-conf.csv"))
vectors <- read_csv(here("common", "names-vectors.csv"))
ru <- st_read(here("common", "ru.geojson"))
